---
title: "RV144 Aids trials"
author: "instr"
date: "April 13, 2016"
output: html_document
---


# Thailand Aids study
```{r include=FALSE}
require(tigerstats)
```

## Introduction

In the late 1980s in Thailand, there was a dramatic increase in the prevalence of infection with the human immunodeficiency virus type 1 (HIV-1) in sentinel surveillance cohorts.1-3 Initially, these groups consisted of injection-drug users and commercial sex workers; they were subsequently expanded to include persons in the general population. By 1995, the overall seroprevalence of HIV-1 reached a peak of 3.7% among conscripts in the Royal Thai Army and of 12.5% among conscripts from Northern Thailand.2,4,5 The Thai Ministry of Public Health responded with an effective HIV-prevention campaign, and the number of new HIV-1 infections per year decreased from an estimated 143,000 in 1990 to 14,000 in 2007.2,4,6-9 The persistence of new infection despite these measures led public health officials to conclude that an HIV vaccine, within the context of a broader HIV-prevention program, was needed for better control of the epidemic.

In the data there are 16,402 people who were given a placebo or aids vaccine.

## Methods and data

Study Design and Population
This study was a community-based, randomized, multicenter, double-blind, placebo-controlled efficacy trial of the prime–boost combination of vaccines containing ALVAC-HIV (vCP1521) (Sanofi Pasteur) and AIDSVAX B/E (Global Solutions for Infectious Diseases). For details regarding the vaccines and placebo, see the Supplementary Appendix, available with the full text of this article at NEJM.org. The study was designed to evaluate two coprimary end points: the prevention of HIV-1 infection and the effect of vaccination on the early viral load after infection. The trial was conducted through facilities of the Thai Ministry of Public Health in Rayong and Chon Buri provinces. From September 2003 through December 2005, a total of 16,402 volunteers were enrolled.
Thai men and women who were between the ages of 18 and 30 years and who were not infected with HIV were recruited from the community without regard to HIV risk (i.e., community risk). Written informed consent was obtained from all volunteers, who were required to pass a written test of understanding. Women were counseled to practice effective contraception until 3 months after the last vaccination; pregnant and breast-feeding women were excluded.

I will use the barchart, percent table, and the Chi-Square Curve to analyze the data.

###Study Design and Population
This study was a community-based, randomized, multicenter, double-blind, placebo-controlled efficacy trial of the prime–boost combination of vaccines containing ALVAC-HIV (vCP1521) (Sanofi Pasteur) and AIDSVAX B/E (Global Solutions for Infectious Diseases). For details regarding the vaccines and placebo, see the Supplementary Appendix, available with the full text of this article at NEJM.org. The study was designed to evaluate two coprimary end points: the prevention of HIV-1 infection and the effect of vaccination on the early viral load after infection. The trial was conducted through facilities of the Thai Ministry of Public Health in Rayong and Chon Buri provinces. From September 2003 through December 2005, a total of 16,402 volunteers were enrolled.
Thai men and women who were between the ages of 18 and 30 years and who were not infected with HIV were recruited from the community without regard to HIV risk (i.e., community risk). Written informed consent was obtained from all volunteers, who were required to pass a written test of understanding. Women were counseled to practice effective contraception until 3 months after the last vaccination; pregnant and breast-feeding women were excluded.

###Primary End Points
HIV-1 Infection
HIV-1 infection was diagnosed in 132 subjects (56 in the vaccine group and 76 in the placebo group) during 52,985 person-years of follow-up in the intention-to-treat analysis, in 86 subjects (36 in the vaccine group and 50 in the placebo group) during 36,720 person-years of follow-up in the per-protocol analysis, and in 125 subjects (51 in the vaccine group and 74 in the placebo group) during 52,985 person-years of follow-up in the modified intention-to-treat analysis. One subject in the placebo group who was identified by hospital record as being seropositive for HIV after dying from Pneumocystis jirovecii pneumonia was included in the analysis before the unblinding of the study. This diagnosis of HIV-1 infection was the only one that occurred outside planned procedures.
We create the following data set

```{r}
groupsize = 16402
subgp = groupsize/2
vacine = c(subgp-51,51)
placebo =  c(subgp-74,74)
results = as.table(cbind(vacine,placebo))
rownames(results) <- c("none","aids")

```



## Results
<!-- You are to add descriptive comments to explain to the reader what the plot is showing !-->

The plot below shows 16,402 peoplw were given an aids vaccine or a placebo. The left side of the chart shows the expected outcome if there was no difference in the aids vaccine and placebo. The right side of the chart shows the actual results. Out of the population, 40% of the people who received the aids vaccine, contracted HIV-1 and 60% of the people who received the placebo contracted HIV-1.

### Graphical results
<!--Display graphical evidence as to the effectiveness of the vaccine with explanations!-->
```{r}
barchartGC(results,type = "percent")
```

This chart shows that the vaccine is effective because 40% of the people who received the vaccine were HIV postive, yet 60% who received the placebo were hiv positive. 


### Numerical Results

<!--Display numerical evidence as to the effectiveness of the vaccine with explanations !--> 

```{r}
colPerc(results)
rowPerc(results)
```

In the numerical table above, I see that 40.80 percent of the people who recieved the vaccine contracted aids, yet 59.20 percent of the people who were given the placebo contracted aids.


## Inferential results

<!--Display inferential evidence as to the effectiveness of the vaccine with explanations and interpretations!-->

```{r}
chisqtestGC(results, graph = TRUE)
```


In this chi-square inferential test, I notice the p value is small: 0.0482 so the data was unlikely to have a true null. The vaccine is effective compared to the placebo because it lowers the amount of aids cases.

## Conclusions

<Summarise your results as to the effectiveness of the vaccine with explanations that could be understood by your mom>

In conclusion, the bar chart shows that 100 percent of the population (16,402 participants) was split into two equal groups(50/50) and given the placebo or aids vaccine. After that, they tested the participants and found that 40% of the people who were given the vaccine tested positive for HIV_1 and 60% of the people given the placebo tested postitive for HIV-1. So less people who received the vaccine, contracted aids. The numerical chart shows similar data because 40.80% who received the vaccine and 59.20% who received the placebo contracted aids. Finally, the last test lists the p value as 0.482 which is low, so we know there isnt a high chance of the vaccine being ineffective. When tested, the vaccine truly was effective for this poulation of people because the rate of contracting aids decreased.